---
title: "02_r_prep"
output: html_document
date: "2023-09-29"
---

## Overview

This script runs **before** `03_main_analyses.ipynb`. It prepares two outputs that
the Python notebook depends on:

1. **CHES** (`data/r_outputs/ches_cleaned.csv`) — cleaned Chapel Hill Expert Survey data
2. **Coalition agreements** (`data/r_outputs/coalitionagree_texts.csv`) — coded coalition
   agreement texts used in Section 3.7 of the Python notebook

Prerequisites: `01_manifesto_pull.Rmd` must have been run first (produces
`data/r_outputs/pulled_manifestoes.csv`).

## Load packages
```{r setup, include=FALSE}
rm(list=ls())
pacman::p_load(quanteda, quanteda.textmodels, tidyverse, readr, ggplot2, rstatix,
               grid, gridExtra, viridis, ggsci, ggpubr, ragg, scales, openxlsx,
               countrycode)

ches <- read_csv("data/ches/1999-2019_CHES_dataset_meansv3.csv")
```

## CHES - Process data

```{r ches}

ches_cleaned <- ches %>%
    rename(country_id=country) %>%
    mutate(
        country = case_when(
            country_id == 1 ~ "Belgium",
            country_id == 2 ~ "Denmark",
            country_id == 3 ~ "Germany",
            country_id == 4 ~ "Greece",
            country_id == 5 ~ "Spain",
            country_id == 6 ~ "France",
            country_id == 7 ~ "Ireland",
            country_id == 8 ~ "Italy",
            country_id == 10 ~ "Netherlands",
            country_id == 11 ~ "United Kingdom",
            country_id == 12 ~ "Portugal",
            country_id == 13 ~ "Austria",
            country_id == 14 ~ "Finland",
            country_id == 16 ~ "Sweden",
            country_id == 20 ~ "Bulgaria",
            country_id == 21 ~ "Czech Republic",
            country_id == 22 ~ "Estonia",
            country_id == 23 ~ "Hungary",
            country_id == 24 ~ "Latvia",
            country_id == 25 ~ "Lithuania",
            country_id == 26 ~ "Poland",
            country_id == 27 ~ "Romania",
            country_id == 28 ~ "Slovakia",
            country_id == 29 ~ "Slovenia",
            country_id == 31 ~ "Croatia",
            country_id == 37 ~ "Malta",
            country_id == 38 ~ "Luxembourg",
            country_id == 40 ~ "Cyprus",
            TRUE ~ NA_character_
        )
    ) %>%
    group_by(country, cmp_id, electionyear) %>%
    summarise(
        ches_lr = mean(lrgen, na.rm=TRUE),
        ches_regions = mean(regions, na.rm=TRUE),
        ches_econ = mean(lrecon, na.rm=TRUE),
        ches_env = mean(environment, na.rm=TRUE),
        ches_eu = mean(eu_position, na.rm=TRUE),
        ches_immgr = mean(immigrate_policy, na.rm=TRUE),
        ches_wf = mean(redistribution, na.rm = TRUE)
    ) %>%
    ungroup() %>%
    rename(party=cmp_id, election=electionyear)


write.csv(ches_cleaned, "data/r_outputs/ches_cleaned.csv", row.names=FALSE)
```

## Prepping data for COALITIONAGREE

```{r coalitionagree}

folder = "data/coalitionagree/Coalition Agreements_coded"
folder_list = list.dirs(path = folder)

all_files <- lapply(folder_list, list.files, pattern=".xlsx")
coalitionagree <- data.frame()
pulled_manifestoes <- read_csv('data/r_outputs/pulled_manifestoes.csv')
for (i in seq_along(all_files)){
    if (length(all_files[[i]]) >1){
        for (j in seq_along(all_files[[i]])){
            if (!is.na(all_files[[i]][j])){
                xlsx <- read.xlsx(paste(folder_list[i], all_files[[i]][j],
                                    sep="/"))
                xlsx$country_init <- rep(stringi::stri_split_regex(all_files[[i]][j],
                                                   pattern="_")[[1]][1],
                                   nrow(xlsx))
                xlsx$cabinet_year = rep(stringi::stri_split_regex(all_files[[i]][j],
                                                   pattern="_")[[1]][2],
                                   nrow(xlsx))
                coalitionagree <- bind_rows(coalitionagree, xlsx)
            }
            
        }
    }
}

coalitionagree <- coalitionagree %>%
    mutate(
        country = countrycode(country_init, origin="iso2c", destination="country.name")
    ) %>%
    filter(country %in% pulled_manifestoes$countryname)

write.csv(coalitionagree, "data/r_outputs/coalitionagree_texts.csv")
```
