---
title: "02_r_prep"
output: html_document
date: "2023-09-29"
---

## Overview

This script runs **before** `03a_main_analyses.ipynb` and `03b_ablation_study.ipynb`. It prepares one output that
the Python notebook depends on:

1. **Coalition agreements** (`data/r_outputs/coalitionagree_texts.csv`) — coded coalition
   agreement texts used in Section 3.6 of `03a_main_analyses.ipynb`

Prerequisites: `01_manifesto_pull.Rmd` must have been run first (produces
`data/r_outputs/pulled_manifestoes.csv`).

## Load packages
```{r setup, include=FALSE}
rm(list=ls())
pacman::p_load(quanteda, quanteda.textmodels, tidyverse, readr, ggplot2, rstatix,
               grid, gridExtra, viridis, ggsci, ggpubr, ragg, scales, openxlsx,
               countrycode)
```

## Prepping data for COALITIONAGREE

```{r coalitionagree}

folder = "data/coalitionagree/Coalition Agreements_coded"
folder_list = list.dirs(path = folder)

all_files <- lapply(folder_list, list.files, pattern=".xlsx")
coalitionagree <- data.frame()
pulled_manifestoes <- read_csv('data/r_outputs/pulled_manifestoes.csv')
for (i in seq_along(all_files)){
    if (length(all_files[[i]]) >1){
        for (j in seq_along(all_files[[i]])){
            if (!is.na(all_files[[i]][j])){
                xlsx <- read.xlsx(paste(folder_list[i], all_files[[i]][j],
                                    sep="/"))
                xlsx$country_init <- rep(stringi::stri_split_regex(all_files[[i]][j],
                                                   pattern="_")[[1]][1],
                                   nrow(xlsx))
                xlsx$cabinet_year = rep(stringi::stri_split_regex(all_files[[i]][j],
                                                   pattern="_")[[1]][2],
                                   nrow(xlsx))
                coalitionagree <- bind_rows(coalitionagree, xlsx)
            }
            
        }
    }
}

coalitionagree <- coalitionagree %>%
    mutate(
        country = countrycode(country_init, origin="iso2c", destination="country.name")
    ) %>%
    filter(country %in% pulled_manifestoes$countryname)

write.csv(coalitionagree, "data/r_outputs/coalitionagree_texts.csv")
```
