---
title: "04_r_prep"
output: html_document
date: "2023-09-29"
---

## Overview

This script runs **after** `03_main_analyses.ipynb`. It uses the preprocessed
manifesto data and processed Twitter data that the Python notebook produces to
run all Wordfish benchmark models used for validation in Step 5.

Prerequisites:
- `03_main_analyses.ipynb` must have been run through at minimum:
  - **Section 3.1** (Data Preparation) — produces `data/py_outputs/manifesto.csv`
  - **Section 3.5** (Twitter fine-tuning) — produces `data/py_outputs/tw_processed.csv`

Outputs (all consumed by `04_visualizations.Rmd`):
- `data/r_outputs/wf_gen_all_countries.csv`
- `data/r_outputs/wf_topic_all_countries.csv`
- `data/r_outputs/wf_ep.csv`
- `data/r_outputs/wf_welfare.csv`
- `data/r_outputs/wf_tw.csv`

## Load packages
```{r setup, include=FALSE}
rm(list=ls())
pacman::p_load(quanteda, quanteda.textmodels, tidyverse, readr, ggplot2, rstatix,
               grid, gridExtra, viridis, ggsci, ggpubr, ragg, scales, openxlsx,
               countrycode)

manifesto <- read_csv("data/py_outputs/manifesto.csv")
manifesto_text_en <- manifesto %>% filter(!countryname %in% c("Iceland", "Spain"))
countries <- unique(manifesto_text_en$countryname)
tw_df <- read_csv("data/py_outputs/tw_processed.csv")
```

## Wordfish - Gen

```{r wf_gen}


all_results <- list()

# Get unique countries in the dataset

# Loop through each country and process it
for (country_name in countries) {
  manifesto_country <- manifesto_text_en %>%
    filter(countryname == country_name)
  print(country_name)
  grouped_texts <- manifesto_country %>%
        group_by(party, election) %>%
        summarise(
          text_new = paste(text_en, collapse = " "),
          num_speeches = n(),
          .groups = "drop"
        ) %>%
        filter(!is.na(text_new))

  dfmat <- corpus(grouped_texts, text_field = "text_new") %>%
               tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
               tokens_remove(stopwords("en")) %>%
               dfm() %>%
               dfm_trim(min_termfreq = 15, max_docfreq = 0.75, docfreq_type = "prop", verbose = TRUE)

  wf_mod <- quanteda.textmodels::textmodel_wordfish(dfmat, dispersion = "poisson", tol=c(1e-4,1e-6))
  
  # Add country name to the results
  results_country <- grouped_texts %>% 
        select(-text_new) %>%
        mutate(
          country = country_name,
          wf_score = wf_mod$theta,
          wf_se = wf_mod$se.theta
        )
  
  # Store the results in a list
  all_results[[country_name]] <- results_country
}

# Combine all results into one data frame
all_results_combined <- bind_rows(all_results)

# Save to CSV file
write_csv(all_results_combined, "data/r_outputs/wf_gen_all_countries.csv")

```



## Wordfish - Topic

```{r wf_env}

all_results <- list()

manifesto_topic <- manifesto_text_en %>% filter(topic %in% c("Economics", "Labour and Social Welfare", "Immigration",
                                                             "European Integration", "Environment - Growth"))
    
for (country_name in countries) {
    print(country_name)
    
    # Filter data by country
    manifesto_country <- manifesto_topic %>%
        filter(countryname == country_name)
        
    # Loop through each topic within the current country
    for (topic_name in unique(manifesto_country$topic)) {
        
        # Print topic name for debugging or tracking purposes
        print(topic_name)
        
        # Filter data by topic and then group by party, election
        grouped_texts <- manifesto_country %>%
            filter(topic == topic_name) %>%
            group_by(party, election) %>%
            summarise(
                text_new = paste(text_en, collapse = " "),
                num_speeches = n(),
                doc_id = cur_group_id(),
                .groups = "drop"
            ) %>%
            filter(!is.na(text_new))
        
        # Create a document-feature matrix (DFM) and clean it
        dfmat <- corpus(grouped_texts, text_field = "text_new", docid_field = "doc_id") %>%
            tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
            tokens_remove(stopwords("en")) %>%
            dfm() %>%
            dfm_trim(min_termfreq = 20, max_docfreq = 0.75, docfreq_type = "prop", verbose = TRUE)
         
        # Run Wordfish model
        wf_mod <- quanteda.textmodels::textmodel_wordfish(dfmat, dispersion = "poisson")
        # Identify documents retained after dfm_trim
        retained_docs <- docnames(wf_mod)
        
        # Filter manifesto_topic to include only retained documents
        grouped_texts <- grouped_texts %>%
            filter(doc_id %in% retained_docs)
        # Prepare results for the current topic within the country
        results_topic_country <- grouped_texts %>%
            select(-text_new) %>%
            mutate(
                country = country_name,
                topic = topic_name,
                wf_score = wf_mod$theta,
                wf_se = wf_mod$se.theta
            )
        
        # Store the results in a list by combining both country and topic names
        all_results[[paste(country_name, topic_name, sep = "_")]] <- results_topic_country
    }
}

# Combine all results into a single data frame
all_results_combined <- bind_rows(all_results, .id = "country_topic")


# Optionally, save the results to a file
write.csv(all_results_combined, "data/r_outputs/wf_topic_all_countries.csv", row.names = FALSE)

```


## Wordfish - Environment Protection

```{r wf_ep}

manifesto_ep <- manifesto_text_en %>% filter(cmp_code == "501")

all_results <- list()
# Loop through each country and process it
for (country_name in countries) {
      manifesto_country <- manifesto_ep %>%
        filter(countryname == country_name)
      print(country_name)
      grouped_texts <- manifesto_country %>%
            group_by(party, election) %>%
            summarise(
              text_new = paste(text_en, collapse = " "),
              num_speeches = n(),
              doc_id = cur_group_id(),
              .groups = "drop"
            ) %>%
            filter(!is.na(text_new))
    
      dfmat <- corpus(grouped_texts, text_field = "text_new", docid_field = "doc_id") %>%
                   tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
                   tokens_remove(stopwords("en")) %>%
                   dfm() %>%
                   dfm_trim(min_termfreq = 10, max_docfreq = 0.75, docfreq_type = "prop", verbose = TRUE)
    
      wf_mod <- quanteda.textmodels::textmodel_wordfish(dfmat, dispersion = "poisson", sparse = TRUE)
      
      # Add country name to the results
      retained_docs <- docnames(wf_mod)
        
        # Filter manifesto_topic to include only retained documents
      grouped_texts <- grouped_texts %>%
            filter(doc_id %in% retained_docs)
      results_country <- grouped_texts %>% 
            select(-text_new) %>%
            mutate(
              country = country_name,
              wf_score = wf_mod$theta,
              wf_se = wf_mod$se.theta
            )
      
      # Store the results in a list
      all_results[[country_name]] <- results_country
}

# Combine all results into one data frame
all_results_combined <- bind_rows(all_results)

# Save to CSV file
write_csv(all_results_combined, "data/r_outputs/wf_ep.csv")

```

## Wordfish - Welfare Expansion/Retrenchment

```{r wf_growth}

manifesto_welfare = manifesto_text_en %>% filter(cmp_code %in% c("504","505"))

all_results <- list()
# Loop through each country and process it
for (country_name in countries) {
      manifesto_country <- manifesto_welfare %>%
        filter(countryname == country_name)
      print(country_name)
      grouped_texts <- manifesto_country %>%
            group_by(party, election) %>%
            summarise(
              text_new = paste(text_en, collapse = " "),
              num_speeches = n(),
              doc_id = cur_group_id(),
              .groups = "drop"
            ) %>%
            filter(!is.na(text_new))
    
      dfmat <- corpus(grouped_texts, text_field = "text_new", docid_field = "doc_id") %>%
                   tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
                   tokens_remove(stopwords("en")) %>%
                   dfm() %>%
                   dfm_trim(min_termfreq = 10, max_docfreq = 0.75, docfreq_type = "prop", verbose = TRUE)
    
      wf_mod <- quanteda.textmodels::textmodel_wordfish(dfmat, dispersion = "poisson", sparse = TRUE)
      
      # Add country name to the results
      retained_docs <- docnames(wf_mod)
        
        # Filter manifesto_topic to include only retained documents
      grouped_texts <- grouped_texts %>%
            filter(doc_id %in% retained_docs)
      results_country <- grouped_texts %>% 
            select(-text_new) %>%
            mutate(
              country = country_name,
              wf_score = wf_mod$theta,
              wf_se = wf_mod$se.theta
            )
      
      # Store the results in a list
      all_results[[country_name]] <- results_country
}

# Combine all results into one data frame
all_results_combined <- bind_rows(all_results)


write.csv(all_results_combined, "data/r_outputs/wf_welfare.csv", row.names = FALSE)

```

## Wordfish - Twitter

```{r wf_tw}

grouped_texts <- tw_df %>%
    group_by(topic, lr) %>%
    summarise(
      text_new = paste(text, collapse = " "),
      num_speeches = n(),
      doc_id = cur_group_id(),
      .groups = "drop"
    ) %>%
    filter(!is.na(text_new))
dfmat <- corpus(grouped_texts, text_field = "text_new", docid_field = "doc_id") %>%
              tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
              tokens_remove(stopwords("en")) %>%
              dfm() %>%
              dfm_trim(min_termfreq = 10, max_docfreq = 0.75, docfreq_type = "prop", verbose = TRUE)

wf_mod <- quanteda.textmodels::textmodel_wordfish(dfmat, dispersion = "poisson")
    
results_tw <- grouped_texts %>% 
    select(-text_new) %>%
    mutate(
      wf_score = wf_mod$theta,
      wf_se = wf_mod$se.theta
    )


write.csv(results_tw, "data/r_outputs/wf_tw.csv", row.names = FALSE)
```
